---
title: "Introduction to rolling devices"
author: "Derek Shue"
date: "November 28, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Roller

The package "roller" simulates the creation of a device with a specified number of sides and correlated probabilities and also simulates rolling that device a number of times. 

## Creating a device

A device can be created with the function device(). If no specifications are added, a device with two sides of numbers 1 and 2 is created, with the probability of each side being 0.5.

```{r}
device <- device()
device
```

Specifications can be added by changing the 'sides' and 'prob' arguments. 

```{r}
device <- device(sides = c('a', 'b'), prob = c(0.7, 0.3))
device
```

```{r}
# die with non-standard sides
weird_die <- device(sides = c('i', 'ii', 'iii', 'iv'), prob = rep(0.25,4))
weird_die
is.device(weird_die)

# create a loaded die
loaded_die <- device(sides = 1:6, prob = c(0.075, 0.1, 0.125, 0.15, 0.20, 0.35))
loaded_die
is.device(loaded_die)
```

## Rolling the device

The roll() function will roll a device a specified number of times and then output a "rolls" object that contains the result of the rolls. 

```{r}
# testing a fair die
fair_die <- device(1:6, rep(1/6,6))
fair_50rolls <- roll(fair_die, times = 50)
fair_50rolls
names(fair_50rolls)
fair_50rolls$rolls
fair_50rolls$sides
fair_50rolls$prob
fair_50rolls$total

# testing a string die
str_die <- device(sides = c('a', 'b', 'c', 'd', 'e', 'f'), prob = c(0.075, 0.1, 0.125, 0.15, 0.20, 0.35))
set.seed(123)
str_rolls <- roll(str_die, times = 20)
names(str_rolls)
str_rolls
```

The summary() function outputs a table containing the sides of the device, the count for each result, and the probabaility associated with each result.

```{r}
summary(fair50)
```

## Plotting roll results

The plot method outputs a barchart of relative frequencies of each roll. 

```{r, fig.show = 'hold'}
plot(fair50)
```

## Additional Methods

You can manipulate a "rolls" object by using the extraction, replacement, and addition methods. 
```{r}
# extracting a value
fair50[50]
# replacing a value
fair50[50] <- 'a'
fair50[50]
# adding additional rolls
summary(fair50)
fair60 <- fair50 + 10
summary(fair60)
```
